Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-08-16 manuscript/manuscript.tex
Added speed comparison in manuscript

\todo{speed comparison between homogeneous and variable density}

>>>>

We have computed the gravity potential, the gradient component $g_z$ and the Marussi tensor component $g_{zz}$ generated by a single tesseroid model with homogeneous and variable density at different heights and recorded their computation times (see Figure \ref{fig:speed-comparison}).
We can see that the homogeneous density code is faster than the new variable density algorithm: up two twice faster.

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/speed-comparison.pdf}
\caption{Computation times for a single tesseroid model with homogeneous and variable density at different heights.}
\label{fig:speed-comparison}
\end{figure}
